---
title: "bb while perception"
output: html_notebook
---


libraries
```{r}
library(dplyr)
library(lme4)
library(brms)
library(ggplot2)
```

read in data
```{r}
df <- read.csv("percepduring.csv", sep = ",", header = TRUE)
```

check data types
```{r}
head(df)
```

subject number should be strings

responseVowel should be factors

responseE should be numeric

group should be factors

contStep should be numeric

biteblock should be factors

trial number should start from 1 insteado of 0


change them accordingly:
```{r}
df$subject_nr <- as.character(df$subject_nr)
df$responseVowel <- as.factor(df$responseVowel)
df$responseE <- as.numeric(df$responseE)
df$group <- as.factor(df$group)
df$contStep <- as.numeric(df$contStep)
df$biteblock <- as.factor(df$biteblock)
df<- df %>% mutate(count_radboudbox_response_BB_test = count_radboudbox_response_BB_test + 1, 
                   count_radboudbox_response_NB_test = count_radboudbox_response_NB_test +1) #so that sequence number counting starts from 1 instead of 0
```

coding in contrast levels
```{r}
df$biteblock <- relevel(df$biteblock, ref = "N")
df$group <- relevel(df$group, ref = "NB")
#centering the constinuum step to step 4 (the middle step)
df$contStep <- df$contStep -4


contrast <- cbind (c(0, 1))
colnames (contrast) <- c("-S+N")
contrasts (table$region) <- contrast
contrast <- cbind (c(+0.5, -0.5))
colnames (contrast) <- c("-Y+O")
contrasts (table$age) <- contrast
```

lmer
```{r}
duringLmer <- glmer(responseE~ contStep  *group * biteblock + (contStep|subject_nr) + (biteblock|subject_nr) + (1|pair), data = df, family = binomial)
summary(duringLmer)
                   
```

```{r}
duringLmer <- glmer(responseE~ contStep*group*biteblock + (contStep|subject_nr)+ (1|pair), data = df,family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))
summary(duringLmer)
                   
```


basic brms

```{r}
during_model <- responseE~ contStep*group*biteblock + (contStep|subject_nr) + (1|pair)
fit <- brm(during_model, data = df, family = bernoulli(),control = list(adapt_delta = 0.999), chains = 4, iter = 10000, warmup = 5000, cores = 2, seed = 1417)
```

```{r}
summary(fit)
```
 exp(-0.53) = 0.588605 : bbY makes the odds of choosing E 0.59 times greater per step than bbN
 
0.588 times greater is difficult to interpret, thus: exp(0.53) = 1.698932: bbN makes the odds of choosing E 1.70 times *smaller* per step than bbN

"The positive effect of trial progression (contStep) on the outcome was significantly attenuated in the bite block condition, as indicated by a negative interaction (β = −0.53, 95% CrI [−0.84, −0.23]). Although the effect of contStep remained positive, its magnitude was substantially reduced when a bite block was present."

The slope for the BB condition is flatter (more uniform? Check single steps? How?)

Plot trace and density:

```{r}
plot(fit)
```

posterior predictive check:

```{r}
pp_check(fit)
```


Check $R^2$

```{r}
bayes_R2(fit)
```


plots

```{r}
#count for number of stimuli in BN group per step
df %>%  filter(group == "BN", biteblock == "Y") %>% 
  count(contStep, responseVowel) #93

#count for number of stimuli in posttest in BB group per step
bigtable %>%  filter(BB == "BB", prepost == "post") %>% 
  count(stepOnCon, responseV) #93

#count for number of stimuli in pretest in NB group per step
bigtable %>%  filter(BB == "NB", prepost == "pre") %>% 
  count(stepOnCon, responseV) #87

#count for number of stimuli in posttest in NB group per step
bigtable %>%  filter(BB == "NB", prepost == "post") %>% 
  count(stepOnCon, responseV) #87

probs <- df %>%
  filter(responseV == "E") %>% 
  count(contStep, responseV, biteblock, group)%>% 
  mutate(
    proportionE = case_when(
      BB == "NB" ~ n/87,
      BB == "BB" ~ n/93)
  )

library(ggplot2)
ggplot(bbstep,aes( x=stepOnCon, y=proportionE,color=BB)) + geom_point() + geom_line() + theme_bw()+scale_color_manual(values=c("#FDE725FF", "#440154FF"))
```

