---
title: "bb while perception"
output: html_notebook
---


libraries
```{r}
library(dplyr)
library(lme4)
library(brms)
```

read in data
```{r}
df <- read.csv("percepduring.csv", sep = ",", header = TRUE)
```

check data types
```{r}
head(df)
```

subject number should be strings

responseVowel should be factors

group should be factors

contStep should be numeric

biteblock should be factors

trial number should start from 1 insteado of 0

change them accordingly:
```{r}
df$subject_nr <- as.character(df$subject_nr)
df$responseVowel <- as.factor(df$responseVowel)
df$group <- as.factor(df$group)
df$contStep <- as.numeric(df$contStep)
df<- df %>% mutate(count_radboudbox_response_BB_test = count_radboudbox_response_BB_test + 1, 
                   count_radboudbox_response_NB_test = count_radboudbox_response_NB_test +1) #so that sequence number counting starts from 1 instead of 0
```

coding in contrast levels
```{r}
df$biteblock <- relevel(df$BB, ref = "NB")
#centering the constinuum step to step 4 (the middle step)
df$contStep <- df$contStep -4
```

basic brms

```{r}
during_model <- responseVowel~
  fit <- 
```

model1 <- responseE~ cstep * prepost * AF * BB + (1|subject_nr) + (1|pair)

fit1 <- brm(model1, data = perc,family = bernoulli(), seed = 446) #setting seed for reproducibility
```

Plot trace and density:

```{r}
plot(fit1)
```

posterior predictive check:

```{r}
pp_check(fit1)
```


summarizing the results:

```{r}
summary(fit1)
```

Check $R^2$

```{r}
bayes_R2(fit1)