---
title: "bb while perception"
output: html_notebook
---


libraries
```{r}
library(dplyr)
library(lme4)
library(brms)
library(ggplot2)
```

read in data
```{r}
df <- read.csv("percepduring.csv", sep = ",", header = TRUE)
```

check data types
```{r}
head(df)
```

subject number should be strings

responseVowel should be factors

responseE should be numeric

group should be factors

contStep should be numeric

biteblock should be factors

trial number should start from 1 insteado of 0

pair should be categorical


change them accordingly:
```{r}
df$subject_nr <- as.character(df$subject_nr)
df$responseVowel <- as.factor(df$responseVowel)
df$responseE <- as.numeric(df$responseE)
df$group <- as.factor(df$group)
df$contStep <- as.numeric(df$contStep)
df$biteblock <- as.factor(df$biteblock)
df$pair <- as.factor(df$pair)
df<- df %>% mutate(count_radboudbox_response_BB_test = count_radboudbox_response_BB_test + 1, 
                   count_radboudbox_response_NB_test = count_radboudbox_response_NB_test +1) #so that sequence number counting starts from 1 instead of 0
```

coding in contrast levels
```{r}
df$biteblock <- relevel(df$biteblock, ref = "N")
contrast <- cbind (c(-0.5, +0.5))
colnames (contrast) <- c("-BN+NB")
contrasts (df$group) <- contrast
#centering the continuum step to step 4 (the middle step) -> changing this to centering on 3, because data shows that 3 is actually the most confusing step
df$contStep <- df$contStep -4

```

gmer
```{r}
duringLmer <- glmer(responseE~ contStep  *group * biteblock + (contStep|subject_nr) + (biteblock|subject_nr) + (1|pair), data = df, family = binomial)
summary(duringLmer)
                   
```

```{r}
duringGlmer <- glmer(responseE~ contStep*group*biteblock + (contStep|subject_nr)+ (1|pair), data = df,family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))
summary(duringGlmer)
                   
```


basic brms

```{r}
during_model <- responseE~ contStep*group*biteblock + (contStep|subject_nr) + (1|pair)
fit <- brm(during_model, data = df, family = bernoulli(),control = list(adapt_delta = 0.999), chains = 2, iter = 5000, warmup = 2000, cores = 2, seed = 1417)
```

```{r}
summary(fit)
#get_prior(fit, data = df)
```
 exp(-0.53) = 0.588605 : bbY makes the odds of choosing E 0.59 times greater per step than bbN
 
0.588 times greater is difficult to interpret, thus: exp(0.53) = 1.698932: bbN makes the odds of choosing E 1.70 times *smaller* per step than bbN

"The positive effect of trial progression (contStep) on the outcome was significantly attenuated in the bite block condition, as indicated by a negative interaction (β = −0.53, 95% CrI [−0.84, −0.23]). Although the effect of contStep remained positive, its magnitude was substantially reduced when a bite block was present."

The slope for the BB condition is flatter (more uniform? Check single steps? How?)

The above was corrected by investigating the repeated data due to open sesame propagation

(releveling to BB=Y as intercept did not change the significance of "group")



Plot trace and density:

```{r}
plot(fit)
```

posterior predictive check:

```{r}
pp_check(fit)
```


Check $R^2$

```{r}
bayes_R2(fit)
```


changing priors
```{r}
# Define Cauchy priors
# Intercept: Cauchy(0, 10)
# Coefficients: Cauchy(0, 2.5)
priors <- c(
  prior(cauchy(0, 10), class = "Intercept"),                
  prior(cauchy(0, 2.5), class = "b")
)
fit2 <- brm(during_model, data = df, 
            prior = priors,
            family = bernoulli(),control = list(adapt_delta = 0.99), chains = 2, iter = 5000, warmup = 2000, cores = 2, seed = 1417)
summary(fit2)
```


plots

```{r}
#count for number of stimuli in NB group per step, in the bite block condition
df %>%  filter(group == "NB", biteblock == "Y") %>% 
  count(contStep, responseVowel) #33 

#count for number of stimuli in NB group per step, in the no bite block condition
df %>%  filter(group == "NB", biteblock == "N") %>% 
  count(contStep, responseVowel) #33

#count for number of stimuli in BN group per step, in the bite block condition
df %>%  filter(group == "BN", biteblock == "Y") %>% 
  count(contStep, responseVowel) #33

#count for number of stimuli in BN group per step, in the no bite block condition
#".drop = FALSE" keeps the zero values in instead of dropping the rows 

probs <- df %>%
  count(contStep, responseVowel, biteblock, group,.drop = FALSE)%>% 
  mutate(
    proportionE = n/33,
    #contStep = contStep+3
  )%>%
  filter(responseVowel == "E") 

#plot each group separately and add instead

library(ggplot2)
ggplot(probs,aes(x=contStep, y=proportionE,color=biteblock, linetype = group))+ geom_point()+ geom_line() + xlab("continuum step") + theme_bw()+ scale_color_manual(values=c("#FDE725FF", "#440154FF"))+ scale_linetype_discrete(labels = c("BB-NB", "NB-BB"))
```
the most confusing step seems to be step 3


Calculating Bayes Factors
```{r}
t = 0.541   # the z value as computed in the glmer model
n1 = 11   # the number of participants in the BN-NB group
n2 = 11   # the number of participants in the NB-BN group

df = n1 + n2 - 2   # the number of degrees of freedom in an independent-samples t test (Rouder et al. 2009, p.234)
n = n1 * n2 / (n1 + n2)   # the "number of participants to use in the computations (Rouder et al. 2009, p.234)

# H1: the effect size is any value around 0 with a chance determined by a Cauchy distribution with typical width half-sqrt-2

width = sqrt(2)/2   # the "width" of the Cauchy distribution of d values; Rouder et al.'s r value

#approximating d for computational ease

d = ((-1000*1e4*width+0.5):(1000*1e4*width-0.5)) / 1e4
weight = 1 / (1 + (d / width) ^ 2)
b04_1 = dt (t, df) / (mean (weight * dt (t, df, ncp = d * sqrt(n))) / mean (weight))
d = ((-2000*1e4*width+0.5):(2000*1e4*width-0.5)) / 1e4
weight = 1 / (1 + (d / width) ^ 2)
b04_2 = dt (t, df) / (mean (weight * dt (t, df, ncp = d * sqrt(n))) / mean (weight))
cat ("B04 = ", b04_2 + (b04_2 - b04_1), "\n")
```

investigating the missing data on step one in the BN group:
```{r}
#filtering for step 1
df |> filter(group == "BN", contStep == 1, biteblock == "Y")
```

calculating washout session length
```{r}
mean(c(693892-322480, 682262-307252, 705015-232774, 674190-283528, 660669-227152, 663954-240138, 666948-279882, 642084-222221, 694059-263705, 701782-269023, 626177-220421, 634641-261478, 686952-264456, 643519-264334, 626734-234760, 610683-218460, 662648-283903, 655900-261221, 677122-251624, 631062-251390, 637778-215591, 681552-290431))
```

